\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-23 icse20/intro.tex
Revised references

Moreover, manual extraction does not scale for frequent updates of the
specification.  While most existing formal semantics and analyzers of
JavaScript support only ECMAScript 5.1 released in December 2009,
from ECMAScript 6, officially dubbed ECMAScript 2015, the 
ECMAScript specification is updated every year.  Focusing on
ECMAScript 5.1 was reasonable until 2014, because the
specification was rarely updated.  However, in late 2014, The Ecma
Technical Committee 39 (TC39)~\cite{tc39} decided to release the
specification annually.  Currently, no formal semantics
nor analyzers for JavaScript correctly deal with recent ECMAScript
features such as lexical binding via \( \code{let} \), the spread
\( \code{...} \) operator, classes, the \( \code{for-of} \) operator,
the \( \code{async} \) functions, and generators.

>>>>

Moreover, manual extraction does not scale for frequent updates of the
specification.  While most existing formal semantics and analyzers of
JavaScript support only ECMAScript 5.1~\cite{ecma5} released in December 2009,
from ECMAScript 6, officially dubbed ECMAScript 2015, the 
ECMAScript specification is updated every year.  Focusing on
ECMAScript 5.1 was reasonable until 2014, because the
specification was rarely updated.  However, in late 2014, The Ecma
Technical Committee 39 (TC39)~\cite{tc39} decided to release the
specification annually.  Currently, no formal semantics
nor analyzers for JavaScript correctly deal with recent ECMAScript
features such as lexical binding via \( \code{let} \), the spread
\( \code{...} \) operator, classes, the \( \code{for-of} \) operator,
the \( \code{async} \) functions, and generators.
